Community Data Science meets Digital Heritage: Controversies about World Heritage Sites in the Online Community of Wikipedia

### 2019-05-09 code/paper.Rmd
up to reverts

```{r}
library(ggrepel)
page_data_for_all_pages %>% 
  select( Site,
          page_wordcount,
         page_wikilinks_in, 
         page_views_last_n_days_total)  %>% 
  ggplot(aes(page_wikilinks_in,
             page_views_last_n_days_total,
             label = str_wrap(Site, 30))) +
  geom_point(alpha = 0.2,
             aes(size = page_wordcount)) +
    geom_text_repel(
    data          = page_data_for_all_pages %>%  
                      filter(page_views_last_n_days_total > 190000),
    segment.size  = 0.2,
    force = 50,
    segment.color = "grey50",
    direction     = "both"
  ) +
  scale_y_log10(expand = c(1, 0.05)) +
  scale_x_log10(limits = c(1, 10000)) +
  coord_fixed(0.5) +
  theme_minimal(base_size = 14) +
  labs(x = "Number of wikilinks to the page",
       y = "Total page views (last 100 days)") +
    ggtitle("Basic qualities about attention given to Wikipedia articles")

ggsave("figures/wh_wikpedia_pages_attention_scatterplot.png")
```

@@

number of edits, total, prop/words
how many bot edits, how many reverts per page
size of edits
diversity of editors

@@

>>>>

```{r}
library(ggrepel)
page_data_for_all_pages %>% 
  select( Site,
          page_wordcount,
         page_wikilinks_in, 
         page_views_last_n_days_total)  %>% 
  ggplot(aes(page_wikilinks_in,
             page_views_last_n_days_total,
             label = str_wrap(Site, 30))) +
  geom_point(alpha = 0.2,
             aes(size = page_wordcount,
                 colour = page_wordcount)) +
    geom_text_repel(
    data          = page_data_for_all_pages %>%  
                      filter(page_views_last_n_days_total > 190000),
    segment.size  = 0.2,
    force = 50,
    segment.color = "grey50",
    direction     = "both"
  ) +
  scale_y_log10(expand = c(1, 0.05)) +
  scale_x_log10(limits = c(1, 10000)) +
  coord_fixed(0.5) +
  scale_color_viridis_c(name = "Wordcount", 
                        labels = c(20000, 15000, 10000, 5000),
                        breaks = c(20000, 15000, 10000, 5000)) +
  scale_size_continuous(name = "Wordcount", 
                        labels = c(20000, 15000, 10000, 5000),
                        breaks = c(20000, 15000, 10000, 5000)) +
   guides(color= guide_legend(), size=guide_legend()) +
  theme_minimal(base_size = 14) +
  labs(x = "Number of wikilinks to the page",
       y = "Total page views (last 100 days)") +
    ggtitle("Basic qualities about the consumption of Wikipedia articles")

ggsave("figures/wh_wikpedia_pages_consumption_scatterplot.png")
```

@@

number of edits, total, edit density (prop/words), size of edits
how many bot edits, how many reverts per page
diversity of editors

@@

Edits per 1k words, as a measure of edit density

```{r}
revision_history_page_details_wordcount <- 
  revision_history_page_details %>% 
  bind_cols(page_data_for_all_pages %>% select(page_wordcount)) %>% 
  mutate(edits_per_1k_words = rh_n_edits / (page_wordcount / 1000))

ten_k_random_wp_pages_revision_history_page_details_summary_tbl_all_dets <- 
bind_cols(ten_k_random_wp_pages, 
          ten_k_random_wp_pages_revision_history_page_details_summary_tbl) %>% 
  mutate(edits_per_1k_words = rh_n_edits / (page_wordcount / 1000))

bind_rows(revision_history_page_details_wordcount %>% 
            select(Site, edits_per_1k_words) %>% 
            mutate(Site = "wh"),
          ten_k_random_wp_pages_revision_history_page_details_summary_tbl_all_dets %>% 
            select(Site, edits_per_1k_words) %>% 
            mutate(Site = "rand")) %>% 
  ggplot(aes(edits_per_1k_words,
             fill = Site)) +
  geom_density(alpha = 0.3) +
  #xlim(0, 100) +
  scale_x_log10() +
  scale_fill_viridis_d(labels = c("Random", 
                               "World Heritage")) +
  labs(x = "Number of edits per 1k words per page",
       fill = "Wikipedia pages") +
  theme_minimal()

ggsave("figures/wh_wikpedia_edits_density_page.png")
```

Size of edits, absolute and raw

```{r}
page_data_for_all_pages_rh_tbl <- 
map_df(page_data_for_all_pages$page_info_t, 
      ~.x$revision_history_page_details, .id = "Site")

label_names <- list(
  "mean_abs_diff"="Absolute edit sizes",
  "mean_diff"="Raw edit sizes"
)

bind_rows(page_data_for_all_pages_rh_tbl %>% 
            select(Site, rh_diff_size) %>% 
            group_by(Site) %>% 
            summarise(mean_diff = mean((rh_diff_size)),
                      mean_abs_diff = mean(abs(rh_diff_size))) %>% 
            mutate(Site = "wh"),
          ten_k_random_wp_pages_revision_history_page_details %>% 
            select(Site, rh_diff_size) %>% 
              group_by(Site) %>% 
            summarise(mean_diff = mean((rh_diff_size)),
                      mean_abs_diff = mean(abs(rh_diff_size))) %>% 
            mutate(Site = "rand")) %>% 
  gather(variable, value, -Site) %>% 
  ggplot(aes(value,
             fill = Site)) +
  geom_density(alpha = 0.3) +
  #xlim(0, 100) +
  scale_x_log10() +
  scale_fill_viridis_d(labels = c("Random", 
                               "World Heritage")) +
  labs(x = "Average size of edits per article (bytes)",
       fill = "Wikipedia pages") +
  facet_wrap( ~ variable, labeller = labeller) +
  theme_minimal()

ggsave("figures/wh_wikpedia_edit_sizes.png")
```

How many edits made by bots? Proportion of edits per page made by bots

```{r}
bind_rows(

page_data_for_all_pages_rh_tbl %>% 
  group_by(Site) %>% 
  summarise( n_bot_edits = sum(bot),
             n_edits = n()) %>% 
  mutate(prop_bot_edits = n_bot_edits / n_edits,
           Site = "wh"),

ten_k_random_wp_pages_revision_history_page_details %>%  
  group_by(Site) %>% 
summarise( n_bot_edits = sum(bot),
           n_edits = n()) %>% 
  mutate(prop_bot_edits = n_bot_edits / n_edits,
         Site = "rand")
) %>%

  ggplot(aes(prop_bot_edits,
             fill = Site)) +
  geom_density(alpha = 0.3) +
  #xlim(0, 100) +
  scale_x_log10() +
  scale_fill_viridis_d(labels = c("Random", 
                               "World Heritage")) +
  labs(x = "Proportion of edits made by bots per article",
       fill = "Wikipedia pages") +
  theme_minimal()

ggsave("figures/wh_wikpedia_edit_sizes.png")
```

Which WH pages are most edited by bots?

```{r}
library(ggrepel)

wh_bots <- 
 tibble(revision_history_page_details = map(page_data_for_all_pages$page_info_t, 
      ~.x$revision_history_page_details))  %>% 
  mutate(Site = page_data_for_all_pages$Site) %>% 
  mutate(n_bot_edits = map_dbl(revision_history_page_details, ~sum(.x$bot)),
         n_edits = map_int(revision_history_page_details, ~nrow(.))) %>% 
  mutate(prop_bot_edits = n_bot_edits / n_edits) %>% 
  arrange(desc(prop_bot_edits))

  ggplot(wh_bots, 
         aes(n_bot_edits,
             n_edits,
             label = str_wrap(Site, 30))) +
  geom_point(alpha = 0.2,
             aes(size =   prop_bot_edits,
                 colour = prop_bot_edits)) +
    geom_text_repel(
    data            = wh_bots %>%  
                      filter(prop_bot_edits > 0.36),
    segment.size  = 0.2,
    force = 50,
    segment.color = "grey50",
    direction     = "both"
  ) +
  scale_y_log10() +
  scale_x_log10() +
  coord_fixed(0.5) +
  scale_color_viridis_c(name = "Proportion of\nedits by bots", 
                        labels = c(0, 0.1, 0.2, 0.3, 0.4),
                        breaks = c(0, 0.1, 0.2, 0.3, 0.4)) +
  scale_size_continuous(name = "Proportion of\nedits by bots", 
                        labels = c(0, 0.1, 0.2, 0.3, 0.4),
                        breaks = c(0, 0.1, 0.2, 0.3, 0.4)) +
   guides(color= guide_legend(), size=guide_legend()) +
  theme_minimal(base_size = 14) +
  labs(x = "Number of edits by bots",
       y = "Total number of edits") +
    ggtitle("Bot activity on Wikipedia articles")

ggsave("figures/wh_wikpedia_pages_bot_edits_scatterplot.png")
```

which bots are most active on WH pages vs random pages?
Cydebot: category edits
Smackbot: dates in templates
ClueBot NG: vandalism

```{r}
bind_rows(
page_data_for_all_pages_rh_tbl %>% 
  filter(bot == 1) %>% 
  group_by(rh_user) %>% 
  tally(sort = TRUE) %>% 
  slice(1:10) %>% 
  mutate( Site = "World Heritage Sites"),

ten_k_random_wp_pages_revision_history_page_details %>% 
  filter(bot == 1) %>% 
  group_by(rh_user) %>% 
  tally(sort = TRUE) %>% 
    slice(1:10) %>% 
   mutate( Site = "Random pages")) %>%

  ggplot(aes(reorder(rh_user, n),
             n)) +
  geom_col() +
  theme_minimal() +
  coord_flip() +
  facet_wrap( ~ Site, scales = "free") +
  xlab("")

ggsave("figures/wh_wikpedia_what_bots.png")
```

So about vandalism? do WH sites get more than random ones?

```{r}
bind_rows(
page_data_for_all_pages_rh_tbl %>% 
  mutate(vandalism = ifelse(str_detect(rh_comment, "vandal"), 1, 0)) %>%
  group_by(Site) %>% 
  summarise( n_vandal_edits = sum(vandalism),
             n_edits = n()) %>% 
  mutate(prop_vandal_edits = n_vandal_edits / n_edits,
           Site = "World Heritage Sites"),

ten_k_random_wp_pages_revision_history_page_details %>% 
  mutate(vandalism = ifelse(str_detect(rh_comment, "vandal"), 1, 0)) %>%
  group_by(Site) %>% 
  summarise( n_vandal_edits = sum(vandalism),
             n_edits = n()) %>% 
  mutate(prop_vandal_edits = n_vandal_edits / n_edits, 
         Site = "Random pages")
) %>%

   ggplot(aes(prop_vandal_edits,
             fill = Site)) +
  geom_density(alpha = 0.3) +
  scale_x_log10() +
  scale_fill_viridis_d(labels = c("Random", 
                               "World Heritage")) +
  labs(x = "Proportion of edits relating to vandalism per article",
       fill = "Wikipedia pages") +
  theme_minimal()

ggsave("figures/wh_wikpedia_vandalism_edits.png")

Which WH pages have the most vandalism?

vandal_edits <- 
 tibble(revision_history_page_details = map(page_data_for_all_pages$page_info_t, 
      ~.x$revision_history_page_details))  %>% 
  mutate(Site = page_data_for_all_pages$Site) %>% 
  mutate(n_vandal_edits = map_dbl(revision_history_page_details, 
                                  ~sum(ifelse(str_detect(.x$rh_comment, "vandalism"), 1, 0))),
         n_edits = map_int(revision_history_page_details, ~nrow(.))) %>% 
  mutate(prop_vandal_edits = n_vandal_edits / n_edits) %>% 
  arrange(desc(prop_vandal_edits))

ggplot(vandal_edits, 
         aes(n_vandal_edits,
             n_edits,
             label = str_wrap(Site, 30))) +
  geom_point(alpha = 0.2,
             aes(size =   prop_vandal_edits,
                 colour = prop_vandal_edits)) +
    geom_text_repel(
    data            = vandal_edits %>%  
                      filter(prop_vandal_edits > 0.055),
    segment.size  = 0.2,
    force = 50,
    segment.color = "grey50",
    direction     = "both"
  ) +
  scale_y_log10() +
  scale_x_log10() +
  coord_fixed(0.5) +
  scale_color_viridis_c(name = "Proportion of\nedits about vandalism", 
                        labels = c(0, 0.025, 0.05, 0.075),
                        breaks = c(0, 0.025, 0.05, 0.075)) +
  scale_size_continuous(name = "Proportion of\nedits about vandalism", 
                        labels = c(0, 0.025, 0.05, 0.075),
                        breaks = c(0, 0.025, 0.05, 0.075)) +
   guides(color= guide_legend(), size=guide_legend()) +
  theme_minimal(base_size = 14) +
  labs(x = "Number of edits about vandalism",
       y = "Total number of edits") +
    ggtitle("Editing about vandalism on Wikipedia articles")

ggsave("figures/wh_wikpedia_pages_vandal_edits_scatterplot.png")

Reverts
